---
title: "Data Preparation"
date: "19/02/2019"
output: html_document
params:
    datafile: "../output/iris.rds"
    outputpath: "../output"
---

```{r setup, include=FALSE}
library(tidyverse)

df_iris <- readRDS(params$datafile)
```



## Data preparation

The loaded data set is the standard `iris` data set converted to a `tibble`:

```{r print-head}
df_iris
```

We change the `Species` variable to a factor:

```{r make-factor}
df_iris$Species <- factor(df_iris$Species)
```

... and plot the petal width by species

```{r boxplot}
ggplot(df_iris, aes(Species, Petal.Width)) +
    geom_boxplot()
```

Since the figure might be needed in a publication, it is good practice
to save it separately:

```{r save-figure}
ggsave("boxplot.png", dpi = 1200, width = 8, height = 5)
ggsave("boxplot.pdf", width = 8, height = 5)
```

Note that the export format / device size might be different from the one
used for the report!

Save the modified data set back to disk:
```{r save-data}
saveRDS(df_iris, sprintf("%s/iris_mod.rds", params$outputpath))
```

In case of multiple figures, it might be worthwhile zipping them:

```{r zip-figures}
figures <- list.files(pattern = "*.(pdf)|(png)$")
zip("figures.zip", files = figures)
unlink(figures)
file.rename("figures.zip", sprintf("%s/figures.zip", params$outputpath))
```

It is also good practice to always print a session info at the end of a report.

```{r session-info}
sessionInfo()
```
